Fair Queuing Aware Congestion Control

### 2022-06-17 tex/paper.tex
Typo

\begin{figure}[h]
\centering
\subfloat[\footnotesize \textbf{Sending} rate at the sender (fair queuing)]{\includegraphics[width=\columnwidth]{{"figures/bw_server_fq"}.pdf}
\label{fig:sender}}\\
\subfloat[\footnotesize \textbf{Receiving} rate at the receiver (fair queuing)]{\includegraphics[width=\columnwidth]{{"figures/bw_client_fq"}.pdf}
\label{fig:receiver}}
\caption{Figure \ref{fig:sender} shows the sending rate, \ref{fig:receiver} the receiving rate in case there's \textbf{fair queuing}. 
Around second 82, the total sending rate is exceeding the link capacity -- 50 Mbit/s -- and fair queuing starts to limit the throughput of the subflow that is sending more. 
Thus, in the lower figure, the dominant subflow and the non-dominant subflow achieve approx.~the same receiving rate even though the dominant subflow sends more (dominant subflow). This is the effect of fair queuing.}
\label{fig:illustration_fq}
\end{figure}

\begin{figure}[h]
\centering
\subfloat[\footnotesize \textbf{Sending} rate at the sender (no fair queuing)]{\includegraphics[width=\columnwidth]{{"figures/bw_server_pfifo"}.pdf}
\label{fig:sender_pfifo}}\\
\subfloat[\footnotesize \textbf{Receiving} rate at the receiver (no fair queuing)]{\includegraphics[width=\columnwidth]{{"figures/bw_client_pfifo"}.pdf}
\label{fig:receiver_pfifo}}
\caption{Figure \ref{fig:sender_pfifo} shows the sending rate, \ref{fig:receiver_pfifo} the receiving rate in case there's \textbf{no fair queuing}. 
Even though the sender sends too much and a queue builds up, still the flow that sends more data also has a higher receiving rate. 
This is in contrast to \autoref{fig:illustration_fq}, where both flows have the same receiving rate once there is congestion at the bottleneck, thanks to fair queuing. }
\label{fig:illustration_no_fq}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\subfloat[\footnotesize \textbf{Sending} rate at the sender (fair queuing)]{\includegraphics[width=\columnwidth]{{"figures/bw_server_fq"}.pdf}
\label{fig:sender}}\\
\subfloat[\footnotesize \textbf{Receiving} rate at the receiver (fair queuing)]{\includegraphics[width=\columnwidth]{{"figures/bw_client_fq"}.pdf}
\label{fig:receiver}}
\caption{Figure \ref{fig:sender} shows the sending rate, \ref{fig:receiver} the receiving rate in case there's \textbf{fair queuing}. 
Around second 82, the total sending rate is exceeding the link capacity -- 50 Mbit/s -- and fair queuing starts to limit the throughput of the subflow that is sending more. 
Thus, in the lower figure, the dominant subflow and the non-dominant subflow achieve approx.~the same receiving rate even though the dominant subflow sends more. This is the effect of fair queuing.}
\label{fig:illustration_fq}
\end{figure}

\begin{figure}[h]
\centering
\subfloat[\footnotesize \textbf{Sending} rate at the sender (no fair queuing)]{\includegraphics[width=\columnwidth]{{"figures/bw_server_pfifo"}.pdf}
\label{fig:sender_pfifo}}\\
\subfloat[\footnotesize \textbf{Receiving} rate at the receiver (no fair queuing)]{\includegraphics[width=\columnwidth]{{"figures/bw_client_pfifo"}.pdf}
\label{fig:receiver_pfifo}}
\caption{Figure \ref{fig:sender_pfifo} shows the sending rate, \ref{fig:receiver_pfifo} the receiving rate in case there's \textbf{no fair queuing}. 
Even though the sender sends too much and a queue builds up, still the subflow that sends more data also has a higher receiving rate. 
This is in contrast to \autoref{fig:illustration_fq}, where both subflows have the same receiving rate once there is congestion at the bottleneck, thanks to fair queuing. }
\label{fig:illustration_no_fq}
\end{figure}
